\documentclass[line, resmargin]{res}
\usepackage[inline]{enumitem}
\usepackage{fontspec}

% Author: Evan Putnam
% This is a resume template that I use for all my job applications.
% Font options are available below for windows/mac fonts (They may or may not work on your system)
% In addittion there are nice margin settings options and dedicated sections.

%%%Windows Font Compile Options%%%
%\setmainfont[ BoldFont={Arialbd.ttf}, ItalicFont={Ariali.ttf},BoldItalicFont={Arialbi.ttf}]{Arial.ttf}
%\setmainfont[ BoldFont={Calibrib.ttf}, ItalicFont={Calibrii.ttf},BoldItalicFont={Calibriz.ttf}]{Calibri.ttf} 

%%%Mac Font Compile Options%%%
\setmainfont[ BoldFont={Helvetica Neue Bold}, ItalicFont={Helvetica Neue Italic},BoldItalicFont={Helvetica Neue Bold Italic}]{Helvetica Neue} 


%Margin settings
\usepackage[bottom=0.0in, top=0.3in]{geometry}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

 
 % For some reason this gives me the format I want when included.  Will debug later...
 
\begin{document}

\name{Evan Putnam \hspace{24.6em} \small github.com/EvanMPutnam }
\address{(484) 554-8487\\ emp9173@rit.edu}

\begin{resume}
\vspace{-7.5mm} %Can reduce space

%State your objective here
\section{OBJECTIVE}
Fourth year Computer Science major looking to apply learned theory and obtain practical experience through full time employment.  Available January 2021.

%This is my education
\section{EDUCATION} 
 Rochester Institute of Technology \\
 Bachelor of Science in Computer Science, December 2020\\
 Minor in Communication\\
 \textbf{GPA:} 3.39
 
%I personally like to have a skills section
\section{SKILLS}
Proficient in C, Java, Python, SQL, Git, AWS, Mac OS, Windows, and Linux. \\
Experience in Swift, C\#, C++, Lua, Javascript, HTML, CSS, Bootstrap, MongoDB, Neo4J, Visual Studio, and Unity3D.
 
 
 %Highlight experience!
\section{EXPERIENCE} 
\textbf{Collins Aerospace Software Engineering Co-Op}, \textit{Cedar Rapids IA} \hfill Sept 2018 - Current \\
Worked in Military Avionics Flight Displays, on a DevOps team, to support the development of software for aircraft display technologies.  Focused primarily on automation of software verification efforts, development of tools to assist other engineers in day to day operations, and continuous build and test both locally as well as in the cloud with AWS.  In addition worked on virtual reality experiences of simulated display software.\\ [10pt]
\textbf{Guardian Life IT and Shared Services Intern}, \textit{Bethlehem PA} \hfill Jun 2018 - Sept 2018 \\
Worked on development of an enterprise Java web application that used Spring MVC, Bootstrap, and JQuery.  In addition, created
data analytics for software incident reports, wrote software to visualize that data, and automated database tasks. \\
\vspace{-5.5mm}


%Student involvement
\section{ACTIVITIES}
\textbf{RIT Space Exploration (RIT SPEX)}\\
Student Director
	\begin{enumerate}
		\item[]In charge of directing a student-faculty research group of 30+ students in various aerospace engineering projects. 
	\end{enumerate}
      
Communication Sub-System and \textdollar 50 Satellite Team Leader
      \begin{enumerate}
        \item[] Responsible for leading a team in the design of a communications sub-system for a small cube satellite.
        \item[] Gathered weather images from NOAA satellites in which antennas were designed and manufactured. Wrote software for automation of data collection.
        \item[] Led a team in the design and preliminary construction of a small satellite based on design from the \textdollar 50SAT - Eagle2 project.
      \end{enumerate}
      

\textbf{Collins Aerospace Student Ambassador}\\
Student Ambassador for Collins Aerospace at RIT.  Responsible for working in conjunction with HR at Collins in recruiting, hosting student events, and acting as a direct point of contact for interactions between Collins and RIT.
      
      
 %Most notable projects
\section{PROJECTS}
\textbf{Augmented Reality Star Viewer}, \textit{WWDC SCHOLARSHIP 2018}\\
Designed and Implemented an Augmented Reality application that won a 2018 WWDC Scholarship from Apple.  The application was created in Swift and used data from the open source HYG-Star database to create an AR walkthrough of the known universe.
\\ [10pt]
\textbf{Meade LX-200 Automation Software}, \textit{RIT SPEX}\\
Designed and wrote software in Python for automation of Meade LX-200 telescope over a wireless network.  Features joystick movement and tracking of low earth orbit satellites with two line elements.
\\ [10pt]
\textbf{Kladoi Language Compiler}, \textit{SCHOOL PROJECT}\\
As a final project for Programming Language Concepts a compiler written in Python was designed and implemented to convert a BASIC-like language to an assembly-like language.


%Coursework
\section{COURSEWORK}
      \begin{enumerate*}[series=MyList, before=\hspace{-0.6ex}, label=\textbullet]
        \item Concepts of Parallel and Distributed Systems
        \item Concepts of Computer Systems
        \item Introduction to Artificial Intelligence
        \item Introduction to Computer Graphics
        \item Operating Systems
        \item Analysis of Algorithms
        \item Principles of Data Management
        \item Programming Language Concepts
        \item Introduction to Software Engineering
        \item Probability and Statistics
        \item Linear Algebra
        \item Business Communications
      \end{enumerate*}

 
\end{resume}
\end{document}
